ROV report

### 2020-03-19 analysis/reports/rov.Rmd
add fia_small

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(dat == "portal_plants")

@@

```
And various metrics of the ROV of the feasible set:

@@

rov_long <- all_di %>%
  select(dat, site, singletons, s0, n0, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts) %>%
  tidyr::pivot_longer(cols = starts_with("mean"),
                      names_to = "rov_index",
                      values_to = "val")
rov_plots <- list()

@@

for(i in 1:length(unique(rov_long$rov_index))) {
  rov_nparts_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val)) +
    geom_point() +
    theme_bw() +
    ggtitle(unique(rov_long$rov_index)[i])
}

@@

>>>>

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(dat == "portal_plants") %>% 
    mutate(binned_nparts = as.factor(ceiling(log_nparts/10)))

@@

Exploring ways we might bin nparts:

```{r nparts distribution}

ggplot(filter(all_di, singletons == F), aes(log_nparts)) +
  geom_histogram(binwidth = 10, boundary = 0, color = "black", alpha = 0) +
  theme_bw()

And various metrics of the ROV of the feasible set:

@@

rov_long <- all_di %>%
  select(dat, site, singletons, s0, n0, skew_percentile, simpson_percentile, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts, binned_nparts) %>%
  tidyr::pivot_longer(cols = starts_with("mean"),
                      names_to = "rov_index",
                      values_to = "val")
rov_plots <- list()

@@

for(i in 1:length(unique(rov_long$rov_index))) {
  rov_nparts_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val)) +
    geom_point() +
    theme_bw() +
    ggtitle(unique(rov_long$rov_index)[i]) +
    geom_vline(xintercept = 10)
}

@@

If we bin nparts:

```{r binned nparts ROV}

rov_nparts_binned_plots <- list()

for(i in 1:length(unique(rov_long$rov_index))) {
  rov_nparts_binned_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(binned_nparts, val)) +
    geom_boxplot() +
    theme_bw()
}

gridExtra::grid.arrange(grobs = rov_nparts_binned_plots)
```

## Percentile distributions

Overall:

```{r percentiles overall}

ggplot(filter(all_di, !singletons), aes(x = skew_percentile)) +
  geom_histogram(bins = 100, boundary = 0) +
  theme_bw()

ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100, boundary = 0) +
  theme_bw()

Binned:

```{r binned percentiles}

ggplot(filter(all_di, !singletons), aes(x = skew_percentile)) +
  geom_histogram(bins = 100, boundary = 0) +
  theme_bw() +
  facet_wrap(vars(binned_nparts))

OK, these visualiations are pretty hard with this dataset (not very many small communities). Try after adding FIA?
